\papertitle

### 2012-10-13 manuscript.tex

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs \naive

@@

The results of our experimental trials verify the results of the Monte Carlo
simulation of the model that we used. The trials that we conducted in
Fig.~\ref{fig:flight_paths_feasible} correspond to the circled region in
Fig.~\ref{fig:heat_map}. The 80\% success rate that we experienced in the
experiments corroborates our calculated probability of success of
approximately 80\%. Additionally the diminished success rate of 50\% near the edges of the viewing triangle that we determined through experimentation supports the reduced probability of success calculated by the simulation.

>>>>

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs.

@@

The results of our experimental trials verify the results of the Monte Carlo
simulation of the model that we used. The trials that we conducted in
Fig.~\ref{fig:flight_paths_feasible} correspond to the circled region in
Fig.~\ref{fig:heat_map}. The 80\% success rate that we experienced in the
experiments corroborates our calculated probability of success of
approximately 80\%. Additionally, the diminished success rate of 50\% near the
edges of the viewing triangle that we determined through experimentation
supports the reduced probability of success calculated by the simulation.
